\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2019-09-14 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
made mervyns changes

Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem. In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections. We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that regression based-methods themselves are indeed projections. As such, this paper is in part a review of existing results cast in a new light. In addition, we also derive three major and novel results.

>>>>

Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem. In this setting, we show that reconciled forecasts have a number of attractive properties when they are obtained via projections. We believe that this is clearer and more intuitive than explanations based on regression modelling. In addition to casting existing results in a new light, the geometric interpretation also allows us to derive three new important results.
